%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{setspace}
\usepackage{fancyhdr}
\renewcommand{\baselinestretch}{1} 
 
\pagestyle{fancy}
\fancyhf{}

 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rory}{Dwyer}{ \urlstyle{same}\href{https://rory-dwyer.com}{rory-dwyer.com} | 
\href{mailto:hello@rory-dwyer.com}{hello@rory-dwyer.com} | 541.324.3716 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     CV Letter
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.26\textwidth} 
\sectionsep
\sectionsep
\sectionsep
\subsection{Portland, Oregon}
\today

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}
\begin{flushleft}
{\setstretch{1.5}\color{blue}


\sectionsep
\sectionsep
\sectionsep
\subsection{To whom it may concern,}
\sectionsep

 It is with great enthusiasm that I submit my application for the position of Graphic Designer and Web Developer for your organization. As a Graphic Designer and Web Developer with over nine years of experience, I know my skills, qualifications and positivity will be assets for your organization. \\
\sectionsep
As you can see from my included resume, I am experienced in web design, graphic design and development. My professional foundation has been built from a myriad of design and programming classes along with professional work at studios and in a freelancing capacity. My client projects include identity branding, marketing and custom websites built from the ground-up. I have designed everything from packaging, advertising campaigns, brochures, posters and booklets and have coded websites and apps. I am familiar and experienced with Adobe CC such as
Photoshop, InDesign, and Illustrator. I am also adept in Javascript, PHP, Wordpress, HTML, CSS and Github. \\
\sectionsep
In addition to being flexible and reliable, I am a team player. I work well with clients and am a strong communicator, presenter and listener. I am experienced with paired programming, design teams and project think tanks. As an employee at your organization Labs my creativity, experien- ce and innovative ideas would serve your business well while I would be afforded the opportunity to strengthen my skillset. \\
I am thrilled at the possibility of being involved with your organization and look forward to hearing back from you. \\
\sectionsep
Sincerely, \\
Rory Dwyer \\
}
\end{flushleft}
\end{minipage}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rory}{Dwyer}{ \urlstyle{same}\href{https://rory-dwyer.com}{rory-dwyer.com} | 
\href{mailto:hello@rory-dwyer.com}{hello@rory-dwyer.com} | 541.324.3716 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.26\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Rogue Community \\ College}
\descript{4 Yr in Computer Science \& Graphic Design}
\location{2014 - 2018}
\sectionsep

\subsection{Online Classes}
\descript{Codecademy, Pluralsight, freeCodeCamp, Youtube}
\location{2014 - Present}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Website:// \href{https://rory-dwyer.com}{\bf rory-dwyer.com} \\
Github:// \href{https://github.com/rorydwyer}{\bf rorydwyer} \\
Dribbble://  \href{https://dribbble.com/Rory-Dwyer}{\bf Rory-Dwyer} \\
Instagram://  \href{https://www.instagram.com/_rorydwyer/}{\bf \_rorydwyer}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Client-Side}
HTML \textbullet{}   CSS \textbullet{} Javascript \textbullet{} JQuery \textbullet{} Vue \textbullet{} React \textbullet{} Blade \textbullet{} NunJucks \textbullet{} SCSS \textbullet{} Bootstrap \textbullet{} Tailwind \textbullet{} Wordpress Plugins \\
\sectionsep

\subsection{Server-Side}
NodeJS \textbullet{} Express \textbullet{} C\# \textbullet{} ASP.net \textbullet{} PHP \textbullet{} Laravel \textbullet{} Roots \textbullet{} MongoDB \textbullet{} MySQL \textbullet{} Shell \\
\sectionsep

\subsection{Operations}
Git \textbullet{} Azure DevOps \textbullet{} Scrum \textbullet{} Agile \textbullet{} Standups \textbullet{} Regression Testing \textbullet{} Selenium \textbullet{} NUnit \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Fun Facts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Fun Facts}
National first place points holder in Fencing (Epee). \\
\paragraphsep
Traveled around the world for skiing and climbing. \\
\paragraphsep
Currently own over 40 house plants. \\

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{TPC Training}
\descript{| Software Developer }
\location{2019 - 2021 | Portland, OR}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Wire framed and developed over 45 pages with a custom Gulp build using Nunjucks and Sass.
\item Singlehandedly researched, prototyped, designed, wrote, and developed an entire sister company (eFoodMobile.com).
\item Implemented homepage and popup A/B tests for increased conversion.
\item Designed web illustrations, flyers, email signatures, infographics, and more.
\item Developed eLearning courses and custom plugins.
\item Designed and developed emails using MJML, and HubSpot templates.
\item Oversaw website optimization, including performance, SEO increases, and mobile responsiveness.
\item Lead overall brand consistency, and designed customer-facing products.
\item Daily collaboration with other developers.
\end{tightemize}
\sectionsep

\runsubsection{Freelance \& Contractor}
\descript{| Web Developer \& Designer }
\location{2013 – Sep 2019 | Ashland, OR \& Portland, OR}

\begin{tightemize}
\item Fluent and extensive experience in HTML, CSS, Sass, PHP, Javascript, Node, JQuery, MYSQL, Wordpress, Vue.js, and React.
\item Responsible for sketching, wire-framing, designing, prototyping, developing, version control, assets, hosting and successful launching of client websites.
\item Successful promotion of brand and company with increase of profits and traffic.
\item Designed and implemented prosperous branding and marketing values.
\item Researched and explored logo concepts that are innovative and stand out from the crowd.
\end{tightemize}
\sectionsep

\runsubsection{MintedKiss}
\descript{| Graphic Designer \& Developer }
\location{2018 – 2019 | Vancouver, WA}
\begin{tightemize}
\item Daily designs for hotel key card advertisements and local businesses with focus on marketing strategy.
\item Extensive branding: highly researched logo, business cards, letterheads, email signatures, apparel, creative guidelines and a concept website.
\end{tightemize}
\sectionsep

\runsubsection{Shasta Networks}
\descript{| Junior Developer}
\location{2014 - 2016 | Ashland, OR}
\begin{tightemize}
\item Worked directly with CEO and Software Engineers integrating new healthcare information systems into company’s network.
\item Coded a firewall for multiple servers using Perl and Bash.
\item Daily use and maintenance of servers through the terminal.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\# NewTab}
\descript{| Developer}
\location{2021 – 2021 | Chrome Extension}
Replaces your new tab with a dashboard featuring a live preview markdown editor, to do list, focus timer, and inspiration. It removes the preview window, \& syntax symbols of markdown providing a live preview while you’re writing.
\paragraphsep
\begin{tightemize}
\item Github:// \href{https://github.com/rorydwyer/NewTab}{\bf rorydwyer/NewTab}
\item Chrome Web Store:// \href{https://chrome.google.com/webstore/detail/newtab/fpmfnjdkdiihflfolajcipeldbicolap}{\bf \# NewTab}
\end{tightemize}
\sectionsep




\end{minipage} 
\end{document}  \documentclass[]{article}
